Competing Bandits: The Perils of Exploration under Competition

### 2018-09-03 paper/content/model.tex

\swedit{For any fixed firm, we say that algorithm 1 \emph{weakly
    dominates} algorithm 2 if algorithm 1 never provides a lower
  market share than than 2 against all opposing strategies. An
  algorithm is a weakly dominant strategy for a firm if the algorithm
  weakly dominates all other algorithms.}

\swcomment{please use the above terminology}

>>>>

\swedit{For any single firm, we say that algorithm 1 \emph{weakly
    dominates} algorithm 2 if algorithm 1 never provides a lower
  market share than than 2 against all opposing strategies. An
  algorithm is a weakly dominant strategy for a firm if the algorithm
  weakly dominates all other algorithms.}
\swcomment{please use the above terminology}

\swedit{todo: tie-breaking}
